Visually pleasing knot projections

### 2022-06-09 inst/jma_rebuttal_review3.tex

Page 4 lines 50-52: No need to differentiate here between over- and
under-strands.  I assume they are treated the same in the optimization
process.

\textcolor{blue}{The referee is correct to say that the over and under
  strand are treated the same by the optimization routine, but my
  intent was to introduce and define the words themselves (rather than
  to differentiate between them).}

Page 4 lines 53-54: ``We would like strand crossing points to be far
from nodes,..."  -- Why?  The curves are also visually continuous across
the nodes!

\textcolor{blue}{The curves certainly are visually continuous across
  the nodes---but only in the optimized knots.  The motivation for
  keeping Bezier nodes far from crossing points is twofold.  Firstly,
  as one traces a curve visually, Bezier nodes cannot possibly avoid
  introducing {\em some} form of disjointness in the path; and such
  disjointness is particularly disruptive if on the understrand of a
  node, as the visual continuity is interrupted.  I have added a
  figure (including two different diagrams of a trefoil knot) to the
  Gallery that illustrates the reason why nodes' being at crossing
  points is undesirable.  In short, at the node of a Bezier curve, the
  radius of curvature undergoes a visually jarring discontinuity which
  looks bad, especially the understrand, which is particularly
  susecptible to such considerations because of the break.  I do
  appreciate that many viewers will find the distinction invisible or
  inconsequential; but my informal polling of family and colleagues
  reveals that, once sensitised to the issue, they cannot unsee the
  kink.  \\ \\ The second reason is more mundane.  With reference to
  figure 8 (the four figure-of-eight knots diagram), we can see a
  vertical line of symmetry on which there are two crossing points.
  Imagine there was a node at one of these crossing points.  There
  would have to be {\em two} nodes at the same point, one for the
  overstrand and one for the understrand; the software would somehow
  have to impose vertical mirror symmetry on the diagram and this
  would necessitate that the knot class contain yet another symmetry
  object, alongside the 12 existing ones.  These considerations become
  yet more onerous when considering rotational symmetry as in Figure 9
  (which shows $5_1$).  If there were a node at, say, the intersection
  of strand 18-19 and 9-10 then somehow the two nodes would have to
  embody not only mirror symmetry (with respect to 5-6/14-15) but also
  fivefold rotational symmetry.  Simply put, this is a nightmare.  The
  software documentation contains a substantial discussion of the
  issue, but I do not believe that the manuscript would benefit from
  what amounts to little more than me grumbling about implementation
  difficulties.}

@@

Page 5 lines 46-51: Why are there SEVEN significant decimal digits?
Does the graphic screen have 10 million pixels per line?

\textcolor{blue}{This is the default print method used by R (which
  internally uses IEC-60559 arithmetic, 14 significant figures).  Any
  attempt by me to change the print method would, I believe, be
  confusing and unnecessary.  The point of the table was to show that
  a knot path could be represented by a few dozen floating-point
  numbers.}

Figure 3, 5, 7: Perhaps fewer than 100 circles per Bezier curve would
be better.

Figure 4.  Knot $7_6$ with strands numbered... -- The main use here seems
to be to see very clearly the extent of every Bezier curve.
Over-/under-crossings seem to become relevant only for the final
rendering of the knot curve with the gaps included.

\textcolor{blue}{Good point, I have added a sentence to this effect to
  the caption of figure 4.\\ \\}

@@

Page 7 line 52: ``The optimization typically proceeds over R 50" - What
is the meaning of this?

\textcolor{blue}{It is a 50-dimensional optimization, optimizing a
  function with fifty parameters (which correspond to different
  positions of Bezier nodes and handles).\\ \\}

@@

Figure 9: The fact that ``angle-crossing penalty" had to be enhanced by
a factor of 100 to achieve a more desirable (in my opinion) result,
illustrates the fact that the "total crossing angles()"-function is
not a good choice for optimization.

\textcolor{blue}{As discussed above, {\tt total\_crossing\_angles()}
  was a somewhat misleading name.  The factor of 100 ensured that even
  tiny deviations from exactly $90^\circ$ were heavily penalised.}

I am missing a description how the two breaks at every crossing point
are being graphically implemented.

\textcolor{blue}{New figure added (Figure 6) which illustrates the implementation}

@@

\textcolor{blue}{ An insightful observation.\\ \\ OLD TEXT In the
  broader context of optimisation in art, we observe that numerical
  optimisation techniques can produce aesthetically pleasing results,
  an observation that might find uptake by graphic artists.\\ \\ NEW
  TEXT In the broader context of optimisation in art, we observe that
  numerical optimisation techniques can produce aesthetically pleasing
  results, an observation that might find uptake by graphic artists.
  Indeed, one could argue that real art lies in the capturing of
  mathematical formulations of aesthetics.  \\ \\ }

Gallery:

Knot diagrams $8_3$ through $8_6$ in Figure 12 stand out with their helices
too tightly wound.  The two criteria on page 4, lines 54 and 55 do not
seem to be sufficiently enforced.  I suggest adjusting these figures
in the spirit of Figure 9b.  This may happen automatically with a
better ``badness function" that penalizes non-orthogonal crossing
angles more directly.

\textcolor{blue}{The referee is correct to say that changing the
  badness function would result in figures less like 9a and more like
  9b.  But I would take issue with the phrase ``too tightly wound''.
  I have polled my colleauges who appear to be evenly split between
  preferring 9a and 9b.  The comparison appears to elicit strong
  opinions here at AUT.  Proponents of 9b point to the broader winding
  along the central helix, while those of 9a point to the more liquid
  and languid appearance, and in particular emphasise the absence of
  retrograde curvature at the bottom.  I have added a brief discussion
  of these issues to the caption of figure 12 [which is now figure 15
    of the resubmission].  I would observe that the {\tt knotR}
  package makes such discussions possible.\\ \\}

### 2022-06-09 inst/jma_knot.tex
fixes #70

With reference to Figure~\ref{k76_strands}, each row of {\tt ou76}
corresponds to a crossing; the first element gives the overstrand and
the second the understrand; thus strand~12 passes over strand~1,
strand~2 passes over strand~11, and so on. The result is shown in
figure~\ref{76_overunder}.

>>>>

With reference to Figure~\ref{k76_strands}, each row of {\tt ou76}
corresponds to a crossing; the first element gives the overstrand and
the second the understrand; thus strand~12 passes over strand~1,
strand~2 passes over strand~11, and so on.  The graphical
implementation is indicated in
Figure~\ref{overundergraphicalimplementation}, and the complete knot
is shown in figure~\ref{76_overunder}.

\begin{figure}[!tbp] % file overundergraphicalimplementation.pdf is
                     % created in file inst/overunder.R
  \centering
\includegraphics[width=4in]{overundergraphicalimplementation}
\caption{Diagram \label{overundergraphicalimplementation} showing the
  graphical implementation of the line breaks distinguishing
  overstrand from understrand at a crossing point.  Top, details of
  technique used, with mask coloured red.  Bottom, same diagram but
  with mask coloured white, illustrating mechanism for production of
  publication-quality knots}
\end{figure}
